---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

Wilson et. al. talk about a variety of "good enough" practices that pertain to R. For example they mention saving the raw data and in certain instances propose making data read-only. As does not change the raw data at hand in analysis pipe-lines it goes hand in hand with preserving the integrity of the original data file. Additionaly, they propose keeping track of changes to data, software, or analysis of the researchers local machine on a platform like dropbox or Github - which goes hand in hand with the R and R studio as it perfectly integrates and can be used with Github to track changes with collaborators and for ones own record keeping.  


3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 
```{r}
sqrt(4^13)
```


4) Push this homework to the GitHub repository for the homework. 





